Numerical simulation of the dynamics of the artificial heart valve

### 2015-05-07 citech-2015/Paper-template/paper.tex
Writing text for citech paper

First group is related to the finite element methods (\cite{taylor}, \cite{zhang}, \cite{black}).

>>>>

First group is related to the finite element methods (\cite{taylor}, \cite{zhang}, \cite{black}). They may well handle
the complex geometry of the heart, bu the necessity to take into account the interaction between the fluid and flexible walls
leads to permanent rebuilding of the computational grid to meet the changing geometry of the object of research.
This results to significant expenses of time and computational resourses.
